Analysis

### 2024-03-13 production/prod_analysis-fix-t5.Rmd
modificaciones gráficos + add percepcion desigualdad

```{css, echo=FALSE}
# /* expandir el espacio del documento*/
body .main-container {
      max-width: 2000px !important;
      width: 2000px !important;
    }
#/* expandir width de la TOC*/
div.tocify {
    width: 22% !important;
    max-width: 331px !important;
    max-height: 102% !important;
}
```

@@

```{r tab-desc, results="asis", warning=FALSE}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               sjlabelled
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))
# Css
st_css()
st_options(lang = "en",
           footnote = NA,
           bootstrap.css = F,
           custom.css = here::here("input/css/dfsummary.css"),
           dfSummary.custom.1 = NA
           )

# Descriptive table __________________________________________________________
df_study1 <- 
  df_study_long_t5_comunas %>% 
  select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) 
# extract variable labels
lab_study1 <- sjlabelled::get_label(df_study1) 
# convert items to factor
for (i in names(select(df_study1,starts_with("in_")))) {
  df_study1[[i]] <- factor(df_study1[[i]],1:5,get_labels(df_study1[[i]]))
}
# set variable labels
df_study1 <- df_study1 %>% na.omit() %>% sjlabelled::set_label(lab_study1)
df_study1$in_amreal <- sjlabelled::set_label(df_study1$in_amreal,label = "Threat (Unemployment increases)")

df<- dfSummary(x = df_study1,
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = TRUE,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = T, # n valido
               # col.widths = c(700,10,10,10,10,10)
               )
# df$Variable <- NULL # delete variable column
view(df,
     file = here::here("output/tables/desc01.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/desc01.html"),
        file =here::here("output/tables/desc01.png")) # Remover archivo HTML
# print(df, method = "render")

individual <- 
  df_study1 %>% 
  select(conviviality, identity,
         in_amreal,
         educ,quintil1,ess,know_inm_t1t4,frien_inm_t1t4)

df_individual<- dfSummary(x = individual,
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = TRUE,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = F,# n valido
               # max.distinct.values = 15,
               max.string.width = 50,
               # col.widths = c(700,10,10,10,10)
               )
df_individual$Variable <- NULL # delete variable column
df_individual <- df_individual %>% rename("Variable"=Label)

view(df_individual,
     file = here::here("output/tables/ds_individual.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/ds_individual.html"),
        file =here::here("output/tables/table2.jpg")) # Remover archivo HTML
# print(df, method = "render")

comunal <- 
  df_study1 %>% 
  select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl, #conviviality
         in_simili,in_amsimb,in_acpier,in_acadop, #identity
         conviviality, identity, 
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  select(inm_prop_cas17_w,inm_prop_cas20_w,dif_inm)

df_municipal<- dfSummary(x = comunal,
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = TRUE,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = F,# n valido
               # max.distinct.values = 15,
               # max.string.width = 50,
               # col.widths = c(700,10,10,10,10)
               )

df_municipal$Variable <- NULL # delete variable column
df_municipal$`Freqs (% of Valid)` <- NULL # delete variable column
df_municipal <- df_municipal %>% rename("Variable"=Label)

view(df_municipal,
     file = here::here("output/tables/ds_municipal.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/ds_municipal.html"),
        file =here::here("output/tables/table3.jpg")) # Remover archivo HTML
# print(df, method = "render")
```

```{r likert}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
# cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               sjlabelled,
               ggplot2,
               ggrepel,
               cowplot,
               sjPlot,
               ggpubr
)
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# Descriptive  __________________________________________________________
df_study1 <- 
  df_study_long_t5_comunas %>% 
  select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,
         educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm)

# para modelar estaba invertido:
#original: fraseo negativo: mayor acuerdo es "negativo" porque se pierde identidad
#recodificado: inversion de valores 5 es "menos perdida". Es positivo.
#ecodificado a sentido original para plot: 5 es "mayor perdida". Es negativo
sjmisc::frq(df_study1$in_amsimb)
sjmisc::frq(sjmisc::rec(df_study1$in_amsimb,rec = "rev"))
df_study1$in_amsimb <- sjmisc::rec(df_study1$in_amsimb,rec = "rev")
# extract variable labels
lab_study1 <- sjlabelled::get_label(df_study1)
# # convert items to factor
# for (i in names(select(df_study1,starts_with("in_")))) {
#   df_study1[[i]] <- factor(df_study1[[i]],1:5,get_labels(df_study1[[i]]))
# }
# set variable labels
df_study1 <- df_study1 %>% na.omit() %>% sjlabelled::set_label(lab_study1)
df_study1$in_amreal <- sjlabelled::set_label(df_study1$in_amreal,label = "Threat (Unemployment increases)")
df_study1$in_amsimb <- sjlabelled::set_label(df_study1$in_amsimb,label = "Loose of identity because of migrants")

df_study1 <- 
  df_study1 %>% 
  select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         in_amreal)
# view_df(df_study1)

# se invierten todos los items para el plot, NO SU SENTIDO  para modelamiento
for (i in names(df_study1)) {
  df_study1[[i]] <- sjmisc::rec(x = df_study1[[i]],rec = "rev")  
}

  # Declare ggplot2 features
  ggplot2::theme_set(ggplot2::theme(panel.background = ggplot2::element_rect(fill = "gray85",
                                                                             colour = "gray85"),
                                    panel.border = ggplot2::element_blank(),
                                    axis.text.y = ggplot2::element_text(size = 13,
                                                                        hjust = 1),
                                    title = ggplot2::element_text(size = 18,
                                                                  face = "bold"),
                                    legend.text = ggplot2::element_text(size = 12),
                                    plot.caption = ggplot2::element_text(size = 10,
                                                                         face = "plain",
                                                                         hjust = 1
                                                                         )
                                    )
                     )
#

#Plot 1: Conviality-----------------------------------------------------------
p1<-
  dplyr::select(df_study1,in_ansied,in_simpat,in_valfam,in_valami,in_amigcl) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Conviviality"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE) +
  ggplot2::theme(legend.position = "none")

#Plot 2: Identity-------------------------------------------------------------
p2<-
  dplyr::select(df_study1,in_simili,in_amsimb,in_acpier,in_acadop) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Identity"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "none")

#Plot 3: Threat---------------------------------------------------------------
p3<-
  dplyr::select(df_study1,in_amreal) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      # title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "none")

#Legend: Extract legend for the final plot using ggpubr
leg<- ggpubr::as_ggplot(
  ggpubr::get_legend(
    dplyr::select(df_study1,in_amreal) %>%
      sjPlot::plot_likert(geom.colors = "PuBu",
                          catcount = 4,
                          cat.neutral = 3) +
      ggplot2::theme(legend.position = "bottom") +
      ggplot2::scale_fill_manual(
        values = c("#b3b3b3ff", "#f1eef6ff", "#bdc9e1ff","#74a9cfff","#0570b0ff"),
        breaks=c("neutral",4,3,2,1),
        labels=c(
          "Neither comfortable nor uncomfortable\nSomewhat\nSomewhat similar\nNeither agree nor disagree\n",
          "Very uncomfortable\nVery little or not at all\nNot similar\nStrongly disagree",
          "Uncomfortable\nA little\nSlightly similar\nDisagree",
          "Comfortable\nQuite a lot\nQuite similar\nAgree",
          "Very comfortable\nA lot\nVery similar\nTotally agree")
      )
  )
)

# plot individuales-----------------------------------------------------------
colors<- c("#b3b3b3ff","#f1eef6ff","#bdc9e1ff","#74a9cfff","#0570b0ff")
p_ansied<-
  dplyr::select(df_study1,in_ansied) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Convivality"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE) + 
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Neither comfortable nor uncomfortable",      
      "Very uncomfortable",
      "Uncomfortable",
      "Comfortable",
      "Very comfortable"
    )
  ) +
  ggplot2::geom_label(label.padding = 1, label.r = 1,label.size = 0.1)

p_ansied[["layers"]]

p_simpat<-
  dplyr::select(df_study1,in_simpat) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      # title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Somewhat ",      
      "Very little or not at all",
      "A little",
      "Quite a lot",
      "A lot"
    )
  )

p_convi<-
  dplyr::select(df_study1,in_valfam,in_valami,in_amigcl) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      # title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom")+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Neither disagree nor agree",      
      "Strongly disagree",
      "Disagree",
      "Agree",
      "Strongly agree"
    )
  )

# Plot individual: IDENTITY -----------------------------------------------
p_simili<-
  dplyr::select(df_study1,in_simili) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Identity"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom")+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Somewhat similar",      
      "Not similiar",
      "Slightly similar",
      "Quite similar",
      "Very similar"
    )
  )

p_identi<-
  dplyr::select(df_study1,in_amsimb,in_acpier,in_acadop,
                in_amsimb) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      # title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom")+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Neither disagree nor agree",      
      "Strongly disagree",
      "Disagree",
      "Agree",
      "Strongly agree"
    )
  )

# Plot individual: THREAT -----------------------------------------------
p_threat<-
    dplyr::select(df_study1,in_amreal) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = c("Threat"),
                      geom.size = 0.8,
                      # axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                      catcount = 4,
                      cat.neutral = 3,
                      grid.range  =  c (1.2 , 1.2),
                      values  =  "sum.outside",
                      reverse.colors = T,
                      reverse.scale = F,
                      show.n = FALSE)  +
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c("neutral", 4, 3, 2, 1),
    labels = c(
      "Neither disagree nor agree",      
      "Strongly disagree",
      "Disagree",
      "Agree",
      "Strongly agree"
    )
  )

# create plot-------------------------------------------------------------------
if (!require("pacman")) install.packages("pacman")
pacman::p_load(cowplot)
s <- 0.4
m <- 0.6
l <- 0.8
#Final plot
title <- cowplot::ggdraw() + 
  cowplot::draw_label(
    "Figure 1: Frequencies for Conviviality, Identity and Threat items",
    fontface = 'bold',
    size = 15,
    x = 0,
    hjust = 0
  )

likert1<-   
  cowplot::add_sub(
    cowplot::plot_grid(title,p_ansied,p_simpat,p_convi,p_simili,p_identi,p_threat, 
                       align = "hv",
                       axis = "a",
                       nrow = 7, #4 plots
                       ncol = 1, #1 column   
                       rel_heights = c(s,s,0.35,m,s,m,s) #fig size within plot
    ),
    label = paste0("Source: Own elaboration based on ELSOC Survey",
                   " (n=",dim(na.omit(df_study1))[1],")"
    ),        # Caption: source and sample size
    size = 12,  # Caption font size
    hjust = -0.25# Caption align  
  ) %>%
  cowplot::ggdraw()  
# likert1
ggplot2::ggsave(filename = "figure1.jpg",
                plot = likert1,
                path = here::here("output/images"),
                device = "jpg",
                units = "cm",
                scale = 3.5,
                width = 10,height = 10)

>>>>

```{css, echo=FALSE}
# /* expandir el espacio del documento*/
body .main-container {
      max-width: 1600px !important;
      width: 1600px !important;
    }
#/* expandir width de la TOC*/
div.tocify {
    width: 22% !important;
    max-width: 331px !important;
    max-height: 102% !important;
}
```

@@

```{r tab-desc, results="asis", warning=FALSE}
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               ggplot2,
               sjPlot,
               tidyverse,
               ggalluvial,
               survey,
               shadowtext
               )
load(file = here::here("input/data-proc/df_study_t6_ind_comunas.RData"))

# Css
st_css()
st_options(lang = "en",
           footnote = NA,
           bootstrap.css = F,
           custom.css = here::here("input/css/dfsummary.css"),
           dfSummary.custom.1 = NA
           )

# Df variables nivel 1
# df<- dfSummary(df_study1_long %>% select(in_simpat:edad),
#                plain.ascii = FALSE,
#                style = "grid",
#                tmp.img.dir = "/tmp",
#                graph.magnif = TRUE,
#                headings = F,  # encabezado
#                varnumbers = F, # num variable
#                labels.col = T, # etiquetas
#                na.col = F,    # missing
#                graph.col = T, # plot
#                valid.col = T, # n valido
#                col.widths = c(700,10,10,10,10)
#                )
# df$Variable <- NULL # delete variable column
# view(df,
#      file = here::here("output/tables/desc01.html")
#      ) # Ver tabla en un archivo HTML
# webshot::webshot(url =here::here("output/tables/desc01.html"),
#         file =here::here("output/tables/desc01.png")) # Remover archivo HTML
# # print(df, method = "render")

# Df variables nivel 1 _________________________________________________________
df_study1 <- df_study_long_t6_comunas %>% dplyr::select(ola,
                                               just_educ, merit_effort, merit_talent,
                                               ahead_family:educ, quintil1:sexo)

df_study1$ola <- factor(df_study1$ola,
         labels = c("2016","2017","2018","2019", "2022"))
df_study1$ola <- 
sjlabelled::set_label(x = df_study1$ola,
                      label = "Wave")

df_study1$sexo <- factor(df_study1$sexo,
         labels = c("Male", "Female"))
df_study1$sexo <- 
sjlabelled::set_label(x = df_study1$sexo,
                      label = "Gender")

for (i in c("just_educ",
            "merit_effort","merit_talent")) {
  df_study1[[i]] <- factor(df_study1[[i]],
                            levels = 1:5,
                            labels = c("Strongly disagree","Disagree",
                                       "Neither disagree nor agree",
                                       "Agree", "Strongly agree"))
}

for (i in c("ahead_family","ahead_educ",
            "ahead_ambition", "ahead_hardwork")) {
  df_study1[[i]] <- factor(df_study1[[i]],
                            levels = 1:5,
                           labels = c("Not at all important",
                                  "A little important",
                                  "Somewhat important",
                                  "Pretty important",
                                  "Very important"))
}

df_study1$just_educ <- 
sjlabelled::set_label(x = df_study1$just_educ, 
                      label = "Education distributive justice")

#
df_study1$merit_effort <- 
sjlabelled::set_label(x = df_study1$merit_effort, 
                      label = "People are rewarded for their efforts")

#
df_study1$merit_talent <- 
sjlabelled::set_label(x = df_study1$merit_talent, 
                      label = "People are rewarded for their intelligence")

#
df_study1$ahead_family <- 
sjlabelled::set_label(x = df_study1$ahead_family, 
                      label = "Coming from a wealthy family")

#
df_study1$ahead_educ <- 
sjlabelled::set_label(x = df_study1$ahead_educ, 
                      label = "Having a good level of education")

#
df_study1$ahead_ambition <- 
sjlabelled::set_label(x = df_study1$ahead_ambition, 
                      label = "Having ambition")

#
df_study1$ahead_hardwork <- 
sjlabelled::set_label(x = df_study1$ahead_hardwork, 
                      label = "Hard work")

lab_study1 <- sjlabelled::get_label(df_study1) 
df_study1 <- df_study1 %>% na.omit() %>% sjlabelled::set_label(lab_study1)

df<- dfSummary(x = dplyr::select(df_study1, ola, just_educ, merit_effort, merit_talent, ahead_hardwork, ahead_educ, ahead_ambition, ahead_family, educ, quintil1, ess, pos_id, edad, sexo),
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = TRUE,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = F, # n valido
               col.widths = c(700,10,10,10)
               )
df$Variable <- NULL # delete variable column
summarytools::view(df,
     file = here::here("output/tables/desc02.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/desc02.html"),
        file =here::here("output/tables/desc02.png")) # Remover archivo HTML
# print(df, method = "render")
```

```{r}
df_study1 <- df_study_long_t6_comunas %>% dplyr::select(idencuesta, ola, ponderador_long_total, segmento, estrato,
                                               just_educ, merit_effort, merit_talent,
                                               ahead_family:educ, quintil1:sexo)
df_study1 <- df_study1[complete.cases(df_study1$segmento), ]

df_study1$just_educ <- factor(df_study1$just_educ,
         labels = c("Strongly disagree", "Disagree", "Neither agree
nor disagree", "Agree", "Strongly agree"))

elsoc_diseno <- svydesign(ids = ~segmento, #muestreo por conglomerado a nivel de manzanas (segmento)
                          strata = ~estrato, #muestreo estratificado a nivel ciudad (estato)
                          weights = ~ponderador_long_total, #ponderador longitudinal
                          nest = TRUE,
                          data = df_study1)

#Paso 1
datos.justeduc <- data.frame((svytable(~just_educ + ola + idencuesta, elsoc_diseno, round = F))) %>% dplyr::filter(Freq>0)  %>% group_by(ola) %>% mutate(porcentaje=Freq/sum(Freq)) %>% na.omit()

#Paso 2
etiquetas.justeduc <- data.frame((svytable(~just_educ + ola, elsoc_diseno, round = F))) %>% group_by(ola) %>% mutate(porcentaje=Freq/sum(Freq)) %>% na.omit() %>% 
  mutate(idencuesta = 1)
```

```{r alluvial}
alluvial_justeduc <- ggplot(datos.justeduc, aes(x = ola, fill = just_educ, stratum = just_educ,
                             alluvium = idencuesta, y = porcentaje))+
    ggalluvial::geom_flow(alpha = .66) + 
    ggalluvial::geom_stratum(linetype = 0) +
    scale_y_continuous(labels = scales::percent) + 
    ylab(label = NULL) +
    xlab(label = NULL) + 
    theme(legend.position = 'top',
          legend.title = element_blank(),
          plot.caption = element_text(hjust = 0)) +
    scale_fill_viridis_d(begin = 0, end = .95, direction = -1, option = 'viridis') +
    geom_shadowtext(data = etiquetas.justeduc, 
              aes(label = ifelse(porcentaje > 0.03 , scales::percent(porcentaje, accuracy = .1),"")),
              position = position_stack(vjust = .5),
              show.legend = FALSE,
              size = 4,
              color = rep('white'),
              bg.colour='grey30')+
  scale_x_discrete(labels = c(2016, 2017, 2018, 2019, 2022))

alluvial_justeduc

ggsave(alluvial_justeduc, file="output/graphs/alluvial_dep.png", height = 7, width = 8)
```

```{r bivariate-plots}
merit_plot <- df_study1 %>% 
  select(ahead_family, ahead_ambition, ahead_educ, ahead_hardwork, merit_talent, merit_effort) %>% 
  sjPlot::plot_stackfrq(weight.by = df_study1$ponderador_long_total,
                        expand.grid =TRUE,
                      geom.colors = 'Spectral',
                      show.total = FALSE, 
                      vjust=rep(c("bottom", "top", "bottom", "top", "bottom"),6),
                      legend.labels = c("Strongly disagree", "Disagree", "Neither agree
nor disagree", "Agree", "Strongly agree"),
                      axis.labels = c("Ahead family", "Ahead ambition", "Ahead education", "Ahead hardwork", "Merit talent", "Merit effort")
                      ) +
  theme_light() +
  theme(legend.position="bottom", text = element_text(size = 14))
merit_plot

ggsave(merit_plot, file="output/graphs/merit_plot.png", height = 7, width = 8)
```

```{r}
colors<- c("#f1eef6ff","#bdc9e1ff","#b3b3b3ff","#74a9cfff","#0570b0ff")
range <- c(.9, .8)

p_effort<-
  dplyr::select(df_study1,
                merit_effort) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      geom.size = 0.8,
                      catcount = 5,
                      grid.range  =  range,
                      show.prc.sign = T,
                      reverse.colors = T,
                      reverse.scale = T,
                      show.n = FALSE,
                      intercept.line.color = "white")  +
  ggplot2::theme(legend.position = "bottom",
    text = ggplot2::element_text(size = 16))+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c(1,2,3,4,5),
  ) +
  theme(legend.position = "none")

p_talent<-
  dplyr::select(df_study1,
                merit_talent) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      geom.size = 0.8,
                      catcount = 5,
                      grid.range  =  range,
                      show.prc.sign = T,
                      reverse.colors = F,
                      reverse.scale = T,
                      show.n = FALSE, 
                      intercept.line.color = "white")  +
  ggplot2::theme(legend.position = "bottom",
    text = ggplot2::element_text(size = 16))+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c(1,2,3,4,5), 
    labels = c(
      "Strongly disagree",
      "Disagree",
      "Neither disagree nor agree",
      "Agree",
      "Strongly agree"
    )
  )

p_hardwork<-
  dplyr::select(df_study1,
                ahead_hardwork) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      geom.size = 0.8,
                      catcount = 5,
                      grid.range  =  range,
                      show.prc.sign = T,
                      reverse.colors = F,
                      reverse.scale = T,
                      show.n = FALSE,
                      intercept.line.color = "white")  +
  ggplot2::theme(legend.position = "bottom",
    text = ggplot2::element_text(size = 16))+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c(1,2,3,4,5),
  ) +
  theme(legend.position = "none")

p_educ<-
  dplyr::select(df_study1,
                ahead_educ) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      geom.size = 0.8,
                      catcount = 5,
                      grid.range  =  range,
                      show.prc.sign = T,
                      reverse.colors = F,
                      reverse.scale = T,
                      show.n = FALSE,
                      intercept.line.color = "white")  +
  ggplot2::theme(legend.position = "bottom",
    text = ggplot2::element_text(size = 16))+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c(1,2,3,4,5),
  ) +
  theme(legend.position = "none")

p_ambition<-
  dplyr::select(df_study1,
                ahead_ambition) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      geom.size = 0.8,
                      catcount = 5,
                      grid.range  =  range,
                      show.prc.sign = T,
                      reverse.colors = F,
                      reverse.scale = T,
                      show.n = FALSE,
                      intercept.line.color = "white")  +
  ggplot2::theme(legend.position = "bottom",
    text = ggplot2::element_text(size = 16))+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c(1,2,3,4,5),
  ) +
  theme(legend.position = "none")

p_family<-
  dplyr::select(df_study1,
                ahead_family) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      geom.size = 0.8,
                      catcount = 5,
                      grid.range  =  range,
                      show.prc.sign = T,
                      reverse.colors = F,
                      reverse.scale = T,
                      show.n = FALSE, 
                      intercept.line.color = "white")  +
  ggplot2::theme(legend.position = "bottom",
    text = ggplot2::element_text(size = 16))+
  ggplot2::scale_fill_manual(
    values = colors,
    breaks = c(1,2,3,4,5),   
    labels = c(
      "Not at all important",
      "A little important",
      "Somewhat 
important",
      "Pretty important",
      "Very important"
    )
  )
```
##### Create plot
```{r}
pacman::p_load(cowplot)
t <- 0.1
s <- 0.45
m <- 0.4
xs <- 0.25

caption <- 
  stringr::str_wrap(
    paste0("Note: Own elaboration based on ELSOC Survey ",
           "(n=",dim(na.omit(df_study1))[1],"). "),
    width = 100)

title <- cowplot::ggdraw() + 
  cowplot::draw_label(
    "Frequencies for meritocracy",
    fontface = 'bold',
    size = 15,
    x = 0,
    hjust = 0
  )

likert1<-   
  cowplot::add_sub(
    cowplot::plot_grid(
                       p_effort,
                       p_talent,
                       p_hardwork,
                       p_educ,
                       p_ambition,
                       p_family,
                       align = "hv",
                       axis = "a",
                       nrow = 7, #6 plots
                       ncol = 1, #1 column   
                       rel_heights = c(
                                       s,s,s,s,
                                       s,
                                       s) #fig size within plot
    ),
    label = "", # Caption: source and sample size
    size = 11,  # Caption font size
    hjust = 0# Caption align 
  ) %>% 
  cowplot::ggdraw()
jpeg(here::here("output/graphs/figure1.jpg"),
    # units = "cm",
    # res = 100,
    width = 800,
    height = 800)
likert1
dev.off()
```

justification education vs year

```{r}
just_educ_year = df_study1 %>%
  group_by(ola) %>%
  summarise(education = mean(just_educ, na.rm = T))

categorias_x <- c(2016, 2017, 2018, 2019, 2022)

educ_year_plot <- just_educ_year_survey %>% ggplot(aes(ola, education)) +
  theme_bw(base_size = 14) +
  geom_point(size = 4)+
  ylab("Justification of inequality") +
  xlab("Wave") +
  scale_x_discrete(labels = categorias_x) +
  ylim(1,3)
educ_year_plot

ggsave(educ_year_plot, file="output/graphs/educ_year_plot.png", width = 7, height = 7)
```

Bivariate descriptive by year

probar ponderadores longitudinales

```{r}
educ_effort_year = elsoc_diseno %>% filter(!is.na(merit_effort)) %>% 
  group_by(ola, merit_effort) %>%
  summarise(education = survey_mean(just_educ, vartype = "ci", na.rm = T)) %>% 
  ungroup()

educ_talent_year = elsoc_diseno %>% filter(!is.na(merit_talent)) %>% 
  group_by(ola, merit_talent) %>%
  summarise(education = survey_mean(just_educ, vartype = "ci", na.rm = T)) %>% 
  ungroup()

categorias_x <- c("Strongly disagree", "Disagree", "Neither agree 
nor disagree", "Agree", "Strongly agree")
categorias_f <- c(2016, 2017, 2018, 2019, 2022)

effort_educ_year_plot <- educ_effort_year %>% 
  ggplot(aes(factor(merit_effort), education, color = factor(ola), shape = factor(ola))) +
  theme_bw(base_size = 14) +
  geom_point(size = 4)+ 
  ylab("Justification of inequality") +
  xlab("Merit: effort") +
  ylim(1, 3) +
  scale_x_discrete(labels = categorias_x) +
  scale_color_discrete(labels = categorias_f, name="Wave") +
  scale_shape_discrete(labels = categorias_f, name="Wave")

effort_educ_year_plot

talent_educ_year_plot <- educ_talent_year %>% 
  ggplot(aes(factor(merit_talent), education, color = factor(ola), shape = factor(ola))) +
  theme_bw(base_size = 14) +
  geom_point(size = 4) +
  ylab("Justification of inequality") +
  xlab("Merit: talent") +
  ylim(1, 3) +
  scale_x_discrete(labels = categorias_x) +
  scale_color_discrete(labels = categorias_f, name="Wave") +
  scale_shape_discrete(labels = categorias_f, name="Wave")

talent_educ_year_plot

ggsave(effort_educ_year_plot, file="output/graphs/effort_educ_year.png", height = 7, width = 7)
ggsave(talent_educ_year_plot, file="output/graphs/talent_educ_year.png", height = 7, width = 7)

educ_effort_year <- educ_effort_year %>% pivot_longer("merit_effort", 
                              names_to="merit", 
                              values_to="value")

educ_talent_year <- educ_talent_year %>% pivot_longer("merit_talent", 
                              names_to="merit", 
                              values_to="value")

educ_merit_year <- rbind(educ_effort_year, educ_talent_year)

custom_labeller <- as_labeller(function(variable, value) {
  return(categorias_f[value])
})
categorias_z <- c("Effort", "Talent")
merit_educ_year <- educ_merit_year %>% 
  ggplot(aes(factor(value), education)) +
  theme_bw(base_size = 14) +
  geom_point(aes(color=merit, shape=merit), size=3) +
  ylab("Justification of inequality") +
  xlab("Merit") +
  ylim(1, 3) +
  facet_wrap(~factor(ola), scales = "free", labeller = custom_labeller) +
  scale_color_discrete(labels = categorias_z, name="Merit") +
  scale_shape_discrete(labels = categorias_z, name="Merit")
merit_educ_year

ggsave(merit_educ_year, file="output/graphs/merit_educ_year.png", height = 7, width = 7)
```
